Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Misc. tweaks for space.

% A category with the (minimum) three required fields
\category{K.3.1}{Computers and Education}{Computer
  Uses in Education}[computer-managed instruction]
\category{I.2.7}{Artificial Intelligence}{Natural Language
  Processing}[narrative interfaces]
\category{H.5.2}{Information Interfaces and Presentation}{User
  Interfaces}[narrative interfaces]
\terms{Design, Human Factors}

@@

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}.  Nell uses a
\textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative,laurel:computers} 
to guide the child user through the pedagogical capabilities of the
system.  All system actions are shaped by the storybook metaphor, and
interactions with the system are conceptualized as interactions with
one of the system protagonists.

@@

In the future, we expect to allow further narrative personalization
via recombination of story elements.
Lebowitz~\cite{lebowitz:universe85} and Riedl~\cite{riedl:planning}
show how a planner can be used to recombine and adapt story fragments.
In this we expect to be less ambitious than the cited work: instead of
attempting to generate thousands of stories from tens of templates, we
expect to select and then modestly adapt from hundreds of story
modules created in a decentralized manner by teachers---and eventually
by the students themselves.

@@

We leverage AIML~\cite{aiml:2005},%
\footnote{Wilcox identifies several shortcomings with the expressive
  power of AIML, proposing ChatScript as a
  replacement~\cite{wilcox:2010}.  At present AIML's community and
  diversity of third-party implementations make it preferable.}
the markup language developed for AliceBot, three-time winner of the
Loebner Prize, a restricted Turing Test competition for chat bots.

@@

<category>
 <pattern>NORTH</pattern>
 <template>
  <javascript>FireEvent(Chat, "North")</javascript>
 </template>
</category>
</aiml>
\end{verbatim}
\caption{An AIML fragment which recognizes the commands \texttt{N},
  \texttt{North}, and \texttt{Go North}. The \texttt{<srai>} tag invokes the
  recognizer recursively.}\label{fig:aiml}
\end{figure}
% show fragment
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.  Figure~\ref{fig:aiml}
illustrates how this can be used to implement a traditional
text adventure interaction for a particular story module.
The child can write instructions such as, ``go north,'' ``go
east,'' or ``open door'' for the agent.  These trigger events
handled by the story module to move the agent through the
adventure---for example, by causing the activity to draw a
new location, causing the agent to describe it, and shifting the
AIML topic to enable vocabulary suitable for the new location.

@@

\section{Acknowledgments}
Nell's design evolved from experience with the Sugar system,
architected by Walter Bender, and through stimulating discussions with
the Sugar community and Angela Chang.
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % paper.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\balancecolumns
% That's all folks!
\end{document}

>>>>

% A category with the (minimum) three required fields
\category{K.3.1}{Computers and Education}{Computer
  Uses in Education}[computer-managed instruction]
%\category{I.2.7}{Artificial Intelligence}{Natural Language
%  Processing}[narrative interfaces]
\category{H.5.2}{Information Interfaces and Presentation}{User
  Interfaces}[narrative interfaces]
\terms{Design, Human Factors}

@@

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}.  Nell uses a
\textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}
to guide the child user through the pedagogical capabilities of the
system.  All system actions are shaped by the storybook metaphor, and
interactions with the system are conceptualized as interactions with
one of the system protagonists.

@@

In the future, we expect to allow further narrative personalization
via recombination of story elements.
Lebowitz~\cite{lebowitz:universe85} and Riedl~\cite{riedl:planning}
show how a planner can be used to recombine and adapt story fragments.
We have less ambition than the cited work: instead of
attempting to generate thousands of stories from tens of templates, we
expect to select and then modestly adapt from hundreds of story
modules created in a decentralized manner by teachers---and eventually
by the students themselves.

@@

@@

<category>
 <pattern>NORTH</pattern>
 <template>
  <javascript>FireEvent(Chat, "North")</javascript>
 </template>
</category>
</aiml>
\end{verbatim}
\caption{An AIML fragment which recognizes the commands \texttt{N},
  \texttt{North}, and \texttt{Go North}. The \texttt{<srai>} tag invokes the
  recognizer recursively.}\label{fig:aiml}
\end{figure}

We leverage AIML~\cite{aiml:2005},
the markup language developed for the three-time Loebner Prize-winning
AliceBot.%
\footnote{Wilcox identifies several shortcomings with the expressive
  power of AIML, proposing ChatScript as a
  replacement~\cite{wilcox:2010}.  At present AIML's community and
  diversity of third-party implementations make it preferable.}
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.

Figure~\ref{fig:aiml}
shows how this can be used to implement a traditional
text adventure interaction for a particular story module.
In this example the child can write instructions such as, ``go north,'' ``go
east,'' or ``open door'' for the agent.  These trigger events
handled by the story module to move the agent through the
adventure---for example, by causing the activity to draw a
new location, causing the agent to describe it, and shifting the
AIML topic to enable vocabulary suitable for the new location.

@@

% CSA: Acknowledge the below in the related work, rather than spending
% space on a heading and a new section.

%% \section{Acknowledgments}
%% Nell's design evolved from experience with the Sugar system,
%% architected by Walter Bender, and through stimulating discussions with
%% the Sugar community and Angela Chang.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % paper.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\balancecolumns
% That's all folks!
\end{document}
